MacLeish: An R package for monitoring environmental conditions in Whately, Massachusetts

### 2022-06-09 joss_paper/paper.Rmd

```{r macleish, echo = FALSE, fig.cap="Map of MacLeish Field Station, Whately, Massachusetts, USA.", out.width="50%"}
knitr::include_graphics(here::here("joss_paper", "macleish_trail_map.jpg"))
```
Figure \ref{fig:macleish} shows a trail map illustrating the MacLeish property.
@Moise:2021 provides an interactive history of the property. 
Research by Smith faculty and students conducted at MacLeish includes 
@guswa2012effect, 
@guswa2012canopy,
@zukswert2014forest, 
@visser2015speeding, 
@bassar2016changes, 
@Wetzel:2017,
@ignace2018decline, 
@jackson2018potential.

@@

The MacLeish Field Station is abundant with scientific inquiry, where the Smith College community explore the diverse ecosystem of plants and animals. The `macleish` package offers access to

1. Data from open-source databases
1. interactive maps of the MacLeish Field Station and surrounding area 
1. Meteorological reading data from historical and current databases 
1. Data on tree diameter of different species infected by the Hemlock Woolly adelgid 
1. A database of images of tree canopy over time

Users may generate usable summary statistics and plots using the data from the `macleish` package.

@@

# Conclusion

The `macleish` package for R has a simple interface that accesses to weather, meteorological, and photographic data to inspire interdisciplinary collaboration among statisticians and ecologists.

>>>>

```{r macleish, echo = FALSE, fig.cap="Map of MacLeish Field Station, Whately, Massachusetts, USA.", out.width="50%"}
knitr::include_graphics(here::here("joss_paper", "macleish_trail_map.jpg"))
```
Figure \ref{fig:macleish} shows a trail map illustrating the MacLeish property.
@Moise:2021 provides an interactive history of the property.

@@

The MacLeish Field Station is rife with scientific inquiry, as the Smith College community explores the diverse ecosystem of plants and animals. 
While numerous research papers, including 
@guswa2012effect, 
@guswa2012canopy,
@zukswert2014forest, 
@visser2015speeding, 
@bassar2016changes, 
@Wetzel:2017,
@ignace2018decline, 
@jackson2018potential
make use of the MacLeish property, the data supporting these research efforts is not centralized or easily accessible to the public.
The `macleish` package offers easy, public access to:

1. spatial data on building, landmarks, streams, trails, and other features of the MacLeish Field Station property 
1. real-time and historical meteorological measurements
1. carefully collected data on tree diameters of different species infected by the Hemlock Woolly adelgid 
1. photographic images of the tree canopy over time

These data are already used in data science textbooks [@baumer2021mdsr] and new research efforts in progress.

@@
